Browsing the Web of Factual Claims

### 2008-09-13 papers/web_of_ideas/web_of_ideas.tex
Minor paper changes. Largely screenshots

\documentclass{sig-alt-release2}
\usepackage{graphicx}
\usepackage{url}
\usepackage{textcomp}
\usepackage{times}
\usepackage{color}

@@

\begin{document}
%
\title{Connecting Documents to Ideas}

\numberofauthors{3}

@@

Much of the information contained on the web consists of opinions, arguments, blogs, articles, and other such unstructured natural language text. Each such document contains one or more statements or ideas that might be of interest to readers.

We propose a new approach to finding, organizing, and sharing ideas contained in web pages. In this approach, a user marks points of interest

@@

@@

% Why thinklink is needed
\section{Motivation?}
1-2pp: 
how do people currently organize, interact, share with web content; 
Thinklink data structures; 
what can people now do with Thinklink

@@

@@

\section{Design}
2pp: describe how the application works and show some screenshots; discuss some implementation decisions
\subsection{Features}
descriptions and screenshots: margin, snippet creation, relationship creation, web UI, point browser
\begin{figure}[ht]
	\includegraphics[scale=0.35]{../screenshots/snippetdialog_sm.jpg}
	\caption{Snippet creation dialog}
	\label{snippetdialog}
\end{figure}

\section{User Studies}
1.5pp: recruitment, environment, tasks, observations, smaller study

@@

@@

@@

\section{Related Work}
1p

\subsection{Argumentation Graphs}

@@

>>>>

\documentclass{chi2009}
\usepackage{times}
\usepackage{url}
\usepackage{graphics}
\usepackage{color}
\usepackage[pdftex]{hyperref}
\hypersetup{%
pdftitle={Browsing the Web of Factual Claims},
pdfauthor={Beth Trushkowski and Rob Ennals},
pdfkeywords={CSCW, sensemaking, web, browsers, collaboration, mind mapping},
bookmarksnumbered,
pdfstartview={FitH},
colorlinks,
citecolor=black,
filecolor=black,
linkcolor=black,
urlcolor=black,
breaklinks=true,
}

@@

\pagenumbering{arabic}  % Arabic page numbers for submission.  Remove this line to eliminate page numbers for the camera ready copy

\begin{document}
% to make various LaTeX processors do the right thing with page size
\special{papersize=8.5in,11in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\pdfpageheight}{\paperheight}
\setlength{\pdfpagewidth}{\paperwidth}
%
\toappear{Submitted for review to CHI 2009.}

\title{Browsing the Web of Factual Claims}

\numberofauthors{2}

@@

Traditional web browsing consists of looking at pages and following links between pages; however when a user browses the web it is often not the pages themselves that they are looking for but the factual claims contained within those documents. A page may contain claims that are contradicted by other pages, or contain one interesting new claim, hidden in a sea of claims that the user has already read. A user must thus invest significant effort extracting the claims that are accurate and interesting from the pages that they look at.
We present Think Link, a tool that links pages to the factual claims that they make, and allows users to browse the web of factual claims, rather than the web of pages.

@@

\keywords{CSCW, sensemaking, web, browsers, collaboration, mind mapping}

\category{H.5.2}{Information Interfaces and Presentation}{User Interfaces}[Graphical User Interfaces]

\begin{figure}[ht]
	\includegraphics[width=8.5cm]{../screenshots/redhighlight.png}
	\caption{Browsing interface, with a contentious claim highlighted}
	\label{redhighlight}
\end{figure}

\begin{figure}[ht]
	\includegraphics[width=8.5cm]{../screenshots/sidebar.png}
	\caption{Browsing interface, with the sidebar opened}
	\label{sidebar}
\end{figure}

\begin{figure}[ht]
	\includegraphics[width=8.5cm]{../screenshots/claim_popup.png}
	\caption{The ``Investigate Claim'' window pops up when one clicks on a claim}
	\label{redhighlight}
\end{figure}

@@

% Why thinklink is needed

@@

\section{Motivation?}
1-2pp: 
how do people currently organize, interact, share with web content; 
Thinklink data structures; 
what can people now do with Thinklink

@@

\section{Related Work}

Diigo lets you save, import, tag, highlight, mark up and share Web pages
	select content on webpage
	share bookmarked content; bookmark url and see what people have tagged on that page
	search over collection of selected content
	tag selected content; social tagging
	see friends activity; more social behavior than necessary (eg. msging)
	meet people ``like'' me?
Stickis
Fleck
Shiftspace
SharedCopy
JKN
MyStickies
DrawHere

- UIs for highlighting
- wikipedia highlighting not trustworthy stuff

\subsection{Web Clippings}

Google Notebook
Trailfire

\subsection{Social Bookmarking}

Shadows

Case-Based reasoning
Sensemaking

\subsection{Argumentation Graphs}
Argumentation graphs express positions and arguments in a formal graph model as nodes and edges, respectively, and are typically used to make a decision or draw a conclusion about some issue. One example implementation is the {\it Zeno} argumentation framework [\idea{cite}], designed for collaborative use in mediation systems to debate the quality of alternative solutions for a problem. In their object model of argumentation elements, based on Rittel's IBIS model [\idea{cite}], example nodes include pro/con arguments, positions, preferences, comments, and decisions. Importantly, arguments are connected via {\it consequent} and {\it antecedent} edges, which are used to inform {\it choices}. The decision-making power of the argumentation graph follows from the traversal of argument relationships to enhance the depth and breadth of understanding about an issue. Our application similarly links claims as {\it supporting} and {\it opposing} other claims to allow users to develop a cohesive understanding of arguments.

Traditional argumentation graphs are designed to solve a specific, isolated issue. Our application supports an ever-expanding set of topics, and arguments can form links between multiple topics. Users can consult the web of ideas directly to form an opinion about a particular issue, but they can also browse for new issues to explore. Opinions or decisions in our model don't have to be static: as the topic is expanded with more supporting and opposing evidence, users may alter previous viewpoints. Another advantage of our model is that the ability to explore claims' source-document evidence is built right into the navigation. Looking at an argument shows both its related argument as well as its supporting {\it snippets}, allowing the user to explore the evidence for himself.

\section{Observations Informing Design}

@@

\section{Interaction Techniques}

\subsection{Features}
descriptions and screenshots: margin, snippet creation, relationship creation, web UI, point browser
\begin{figure}[ht]
	\includegraphics[scale=0.35]{../screenshots/snippetdialog_sm.jpg}
	\caption{Snippet creation dialog}
	\label{snippetdialog}
\end{figure}

\section{Preliminary User Feedback}

1.5pp: recruitment, environment, tasks, observations, smaller study

@@

\idea{remove confusion about ``where i am'' with fisheye view of current claim}

@@

@@

\bibliographystyle{abbrv}
\bibliography{biblio.bib}
